### 2018-07-30 other_R_code/article_selection_process.Rnw
further result classification write-up

\begin{document}

@@

@@

Algorithm:
\begin{enumerate}
  \item use classifier on $R$ and $S$ to identify two lists of keywords
  \item generate probability from classifier parameters
  \item add to keyword list based on probability
\end{enumerate}

>>>>

\begin{document}
<<loadpackages, echo=FALSE, warning=FALSE, message=FALSE>>=
library(durhamevp)
library(tidyverse)
@

@@

\section{The data}
<<loaddata, cache=TRUE, tidy=TRUE>>=
classdocs<-durhamevp::get_classified_docs()
classified_corpus<-quanteda::corpus(classdocs[,c("fakeid", "ocr", "EV_article")], text_field = "ocr")
classified_dfm <- preprocess_corpus(classified_corpus, stem=FALSE, min_termfreq=20, min_docfreq = 10)
@

In the data there are \Sexpr{nrow(classdocs)} cases:
\begin{itemize}
  \item \textbf{\Sexpr{sum(classdocs$election_article==0)}} non-election articles.
  \item \textbf{\Sexpr{sum(classdocs$EV_article==1)}} election violence articles.
  \item \textbf{\Sexpr{sum(classdocs$just_election==1)}} election (but not violent) articles.
\end{itemize}

@@

Algorithm:
\begin{enumerate}
  \item use classifier on $R$ and $S$ to identify two lists of keywords
  \item generate probability from classifier parameters
  \item add to keyword list based on probability
\end{enumerate}
<<findkeywords>>=
keywords<-nb_keywords(classified_dfm, "EV_article")
knitr::kable(head(keywords, 20))
@

\section{Refinement Using Description}

<<usingdescription>>=
description_corpus<-quanteda::corpus(classdocs[,c("fakeid", "description", "EV_article")], text_field = "description")
description_dfm <- preprocess_corpus(description_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)

both_dfms<-split_dfm(description_dfm, n_train = 1500)
nb<-quanteda::textmodel_nb(both_dfms$train, y=quanteda::docvars(both_dfms$train, "EV_article"), prior="uniform")
prob_nb<-predict(nb, newdata = both_dfms$test, type="probability")
pred_nb<-data.frame(predict(nb, newdata = both_dfms$test, type="class"))
res<-data.frame(predict_nb=pred_nb, prob_nb)
names(res)<-c("predict_nb", "prob_notev", "prob_ev")
assess_classification(organise_results(both_dfms$test, res)) %>%
  filter(rowname %in% c("Precision", "Recall", "F1")) %>%
  kable()
@

\section{Refinement Using OCR}

<<usingocr>>=
ocr_corpus<-quanteda::corpus(classdocs[,c("fakeid", "ocr", "EV_article")], text_field = "ocr")
ocr_dfm <- preprocess_corpus(ocr_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)

both_dfms<-split_dfm(ocr_dfm, n_train = 1500)
nb<-quanteda::textmodel_nb(both_dfms$train, y=quanteda::docvars(both_dfms$train, "EV_article"), prior="uniform")
prob_nb<-predict(nb, newdata = both_dfms$test, type="probability")
pred_nb<-data.frame(predict(nb, newdata = both_dfms$test, type="class"))
res<-data.frame(predict_nb=pred_nb, prob_nb)
names(res)<-c("predict_nb", "prob_notev", "prob_ev")
assess_classification(organise_results(both_dfms$test, res)) %>%
  filter(rowname %in% c("Precision", "Recall", "F1")) %>%
  kable()
@
